---
title: "Homework 3"
author: "Vivian Du"
date: "4/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(languageR)
library(knitr)
library(ggplot2)
library(dplyr)
```


Problem 1:
```{r data}
rd = read.table('Robins_data.txt', header=TRUE, strip.white=TRUE)
rd$newage = factor(rd$age, levels = c(1,2,4,5), labels =
c("teens","twenties","forties","fifties"))
rd$lvoc = factor(rd$l, levels = c(1,3), labels =
c("unvocalized","vocalized"), exclude=c(2))

```

I will create a contigency table to compare the observed kind of vocalization in every age group.

```{r contigency}
rd.sub = filter(rd, lvoc %in% c("unvocalized","vocalized") & newage %in% c("teens","twenties","forties","fifties"))

tab = xtabs (~newage + lvoc, data = rd.sub)
tab
```

Now I will compare by calculating the expected counts.

```{r expected}
n = sum(tab)

pUnvocal = sum(tab[, 'unvocalized'])/n
pVocal = 1 - pUnvocal

pTeen = sum(tab['teens',])/n
pTwent = sum(tab['twenties',])/n
pForty = sum(tab['forties',])/n
pFifty = sum(tab['fifties',])/n

531*pUnvocal*pTeen
531*pVocal*pTeen
531*pUnvocal*pTwent
531*pVocal*pTwent
531*pUnvocal*pForty
531*pVocal*pForty
531*pUnvocal*pFifty
531*pVocal*pFifty
```

My expected values are not the same as my observed values.

I will use a chi-square test to check that certain vocalization depends on the age group.

```{r test}
chisq.test(tab)
```

Since the p-value is less than 0.05, I reject the null and conclude that type of vocalization is not independent from age group.

According to the table, the "twenties" group shows the greatest tendency to vocalize.

Problem 2:
(i) Modified stepwise selection
```{r model0}
mod0 = glm(lvoc ~ newage + gender + conscious, data=rd, family= "binomial")
summary(mod0)
```

Remove gender because the p-value > 0.05.

```{r model1}
mod1 = glm(lvoc ~ newage + conscious, data=rd, family= "binomial")
summary(mod1)
```

This is the final model because although some predictors are not significant for all levels, it is for one.

(ii) Final Model Prediction

```{r modelprediction}
prediction_prop = 2.7182^(-(1-0.1925))
prediction_prop

```

```{r actualresults}
f1 = rd[rd$gender == "female",]
f2 = f1[f1$conscious == "connect",]
f3 = f2[f2$newage == "teens",]
total = nrow(f3)
f4 = f3[f3$lvoc == "vocalized",]
prop = nrow(f4)
actual_prop = prop/total
actual_prop

```

The actual proportion of female connect conscious teens who vocalized is 0.079.

Problem 3:
(i)

```{r calculate}
0.25*0.25*0.25*0.75

0.5*0.5*0.5*0.5

0.75*0.75*0.75*0.25
```

L(1/4) = 0.01171875

L(1/2) = 0.0625

L(3/4) = 0.1054688

L(1) = 0

(ii)

When h is 3/4, L(h) has the biggest value. This makes intuitive sense because if the coins is actually biased towards heads with a 75% chance per flip, having the model parameter as 75% towards heads matches the true probability of obtaining heads.

(iii)

The general formula for L(h) is: h^3*(1-h)


